---
title: "Motor Car Trends - Miles Per Gallon vs. Weight"
author: "Anand Narasimhan"
date: "6/17/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
```

## Miles Per Gallon vs. Weight

We'll use the `mtcars` data set that comes with R and display a basic box plot using plot.ly. Some pre-requisites before running this file is to load the plot.ly library.

```{r eval=FALSE}
require(devtools)
install_github("ropensci/plotly")
```

## `mtcars` data

We'll do a quick summary of the `mtcars` data `wt` and `mpg` variables before we plot the data.

```{r echo=FALSE}
data(mtcars)
summary(mtcars[,c(1,6)])
```

Let's also look at the various cyclinders in the data.

```{r echo=FALSE}
table(mtcars$cyl)
```

## Mile Per Gallon  vs Weight

Lets plot Miles per Gallon `mpg` with Weight `wt`

```{r message=FALSE,echo=FALSE}
library(plotly)
p <- plot_ly(data = mtcars, x = ~mpg, y = ~wt,color = ~cyl)
p
```

## Mile Per Gallon  vs Weight - The code

The R code to plot Miles per Gallon `mpg` with Weight `wt` is below

```{r message=FALSE,eval=FALSE}
library(plotly)
p <- plot_ly(data = mtcars, x = ~mpg, y = ~wt,color = ~cyl)
p
```

